Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-10-01 doc/paper.tex
polishing + questions

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}   
    \subsection{A hybrid of the Greedy and shaking}
    \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
    \subsection{A Hybrid of the Greedy + CPLEX}
        CPLEX will soon or later degrade in its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over interactions  and use CPLEX to make the (partial)  solution complete. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations and obtain a partial solution $C$ (therefore, $|C| = K$); 
        	\item Take solution $C$ and make it complete via. CPLEX model. 
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-problem which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$. 
        \end{enumerate}
      \begin{comment}

>>>>

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}   
    \subsection{A hybrid of the Greedy and shaking}
    \fxnote{TODO: Ubaciti pricu o shaking $-->$ Dragan?}
    \subsection{A Hybrid of the Greedy + CPLEX}
        CPLEX will soon or later degrades its performance w.r.t. instance size. On the other hand, the later stage of Greedy increase the chance to worsen the final greedy solution.  So it makes sense to combine  partial solutions generated by  Greedy over a few interactions  and then to use CPLEX up to completion of the partial solution. Our approach consists of the following steps:
        \begin{enumerate}
        	\item Run a Greedy method up to $K$ iterations (parameter) to obtain a partial solution $C$ (therefore, $|C| = K$); 
        	\item Take solution $C$ and make it complete via. CPLEX model. 
        	\begin{itemize}
        		\item CPLEX solves corresponding sub-model which is formed by adding constraints $x_{p_i} = 1$, for all $p_i \in C$ into the existing WOAGP model;
        		\item we obtain a complete solution $C'$;
        	\end{itemize}
            \item return $f(C')$. 
        \end{enumerate}
      \begin{comment}
